---
jupyter:
  jupytext:
    text_representation:
      extension: .Rmd
      format_name: rmarkdown
      format_version: '1.1'
      jupytext_version: 1.2.4
  kernelspec:
    display_name: R
    language: R
    name: ir
---

# POP2 loss model  BET


Organised version of New Horizons analysis. 

Don't include reference as had previously decided to remove it as became too complicated - reference binary is correlated with balance - another way of describing balance.

This is analysis of bet behaviour (higher or lower than participant median) after a loss outcome.

Have excluded participants who don't change their bet.


```{r}
import_library = function(lib_name){
    suppressWarnings(suppressMessages(require(lib_name, character.only = TRUE)))
}

import_library('Hmisc') # for rcorr
import_library('car') # regression diagnostics
import_library('MASS') # residuals?
import_library('boot')
import_library('ggplot2')
import_library('pastecs')
import_library('caTools')
import_library('RColorBrewer')
import_library('corrplot')
import_library('tidyverse')
import_library('robustbase')

source(file="../../../../../POP_functions.R")
source(file="../../../../../glmPost.R")
```

```{r}
modeldata=load_data('BET', 'loss','POP2')
```

## Variable correlations

```{r}
cor_matrix<-modeldata[,c("sqrtTrial.no","Final.balance","logLoss.streak")]

cor(cor_matrix)

vifmodel<-glm(Next.bet.binary~Participant.f
             + sqrtTrial.no 
             + Final.balance
             + logLoss.streak
            ,data=modeldata,family=binomial())
vif(vifmodel)
```

## Model

```{r}
model1<-glm(Next.bet.binary~Participant.f
             + sqrtTrial.no
             + Final.balance
             + Final.balance:group
             + logLoss.streak
             + logLoss.streak:group
             -1
            ,data=modeldata,family=binomial())
print.mod.summary(model1,modeldata)
```


## Robust model

```{r}
robmodel1<-glmrob(Next.bet.binary~Participant.f
             + sqrtTrial.no
             + Final.balance
             + Final.balance:group
             + logLoss.streak
             + logLoss.streak:group
             -1,
               family=binomial, data=modeldata,method="Mqle")

summary(robmodel1)
```

```{r}
robustmodel<-tidy.glmrob(robmodel1,conf.int=TRUE)

robustmodel$OR<-exp(robustmodel$estimate)
robustmodel$OR.low<-exp(robustmodel$conf.low)
robustmodel$OR.high<-exp(robustmodel$conf.high)

write.table(tail(robustmodel,5),"robust_model.csv",sep=",")


data<-(tail(robustmodel,5))
data<-data[,c(1,8,9,10,5)]

data<-rename_cols_for_tables(data)  
data<-rename_rows_for_tables(data)  

filename = "POP2_robmodel_loss_BET"
title = "Experiment 1b: Predicting bet size after a loss"
pcol="p value"

apa_table(data,filename=filename,pcol=pcol,title=title,column_header=names(data))
```

## Check weights

```{r}
modeldata_withweights<-robmodel_weights(modeldata,robmodel1,'BET')
modeldata$rweights<-modeldata_withweights$rweights

robust_diagnostics(model1,robmodel1)
```

## Diagnostics

```{r}
nullmodel<-glm(Next.bet.binary~Participant.f-1,data=modeldata,family=binomial())
data4diagnostics<-glmPost(model1,modeldata,nullmodel)
write.table(data4diagnostics,"data_with_diagnostics.csv",sep=",")
```

```{r}
glmPostfigs(model1,data4diagnostics,0)
```

## Subset model

```{r}
subset_modeldata<-subset(modeldata, Participant.f!= 6 | Participant.f!= 7 | 
                         Participant.f!= 12 |  Participant.f!= 14 |  Participant.f!= 19 |
                         Participant.f!= 59)

robmodel1b<-glmrob(Next.bet.binary~Participant.f
             + sqrtTrial.no
             + Final.balance
             + Final.balance:group
             + logLoss.streak
             + logLoss.streak:group
             -1,
               family=binomial, data=subset_modeldata,method="Mqle")

summary(robmodel1b)
```

## Predicted probs for plotting

```{r}
predicted<-expand.grid(Participant.f=unique(modeldata$Participant.f),
                       group=unique(modeldata$group),
                       Final.balance=c(0,10,20,30,40,50,60),
                       logLoss.streak=c(0,1,2,3,4),
                       sqrtTrial.no=median(modeldata$sqrtTrial.no))
predicted$predicted<-predict(model1,predicted ,type="response")
write.table(predicted,"matrix_predicted.csv",sep=",")


predicted<-expand.grid(Participant.f=unique(modeldata$Participant.f),
                       group=unique(modeldata$group),
                       Final.balance=c(0,10,20,30,40,50,60),
                       logLoss.streak=c(0,1,2,3,4),
                       sqrtTrial.no=median(modeldata$sqrtTrial.no))
predicted$predicted<-predict(robmodel1,predicted ,type="response")
write.table(predicted,"robust_matrix_predicted.csv",sep=",")
```

## Game mode

```{r}
unique_table<-modeldata %>% distinct(Participant, .keep_all = TRUE)

unique_table %>% group_by(group,Game_mode) %>% tally()
```

```{r}
model2<-glm(Next.bet.binary~Participant.f
             + sqrtTrial.no
             + Final.balance
             #+ Final.balance:group
             +Final.balance:Game_mode
             + logLoss.streak
             #+ Loss.streak:group
             + logLoss.streak:Game_mode
             -1
            ,data=modeldata,family=binomial())
print.mod.summary(model2,modeldata)

```

```{r}
robmodel2<-glmrob(Next.bet.binary~Participant.f
             + sqrtTrial.no
             + Final.balance
             #+ Final.balance:group
             +Final.balance:Game_mode
             + logLoss.streak
             #+ Loss.streak:group
             + logLoss.streak:Game_mode
             -1,
               family=binomial, data=modeldata,method="Mqle")
summary(robmodel2)
```

```{r}

```
