---
jupyter:
  jupytext:
    text_representation:
      extension: .Rmd
      format_name: rmarkdown
      format_version: '1.1'
      jupytext_version: 1.2.4
  kernelspec:
    display_name: R
    language: R
    name: ir
---

# POP1 win model BET
Organised version of New Horizons analysis. DID NOT EXCLUDE p24 now - decided it was wrong to exclude as although finished early, behav before interesting. 
Don't separate wins and LDWs.
Don't include reference as had previously decided to remove it as became too complicated - reference binary is correlated with balance - another way of describing balance.

This is analysis of bet behaviour (higher or lower than participant median) after a win outcome. There are limited number of bet changes in these data, so these models aren't very powerful. Have excluded participants who don't change their bet. A lot of warning messages for pred probs close to zero or one. 

```{r}
import_library = function(lib_name){
    suppressWarnings(suppressMessages(require(lib_name, character.only = TRUE)))
}

import_library('Hmisc') # for rcorr
import_library('car') # regression diagnostics
import_library('MASS') # residuals?
import_library('boot')
import_library('ggplot2')
import_library('pastecs')
import_library('caTools')
import_library('RColorBrewer')
import_library('corrplot')
import_library('tidyverse')
import_library('robustbase')

source(file="../../../../../POP_functions.R")
source(file="../../../../../glmPost.R")
```

```{r}
modeldata=load_data('BET','win','POP1')
```

## Variable correlations

```{r}
cor_matrix<-modeldata[,c("sqrtTrial.no","logResult","Final.balance")]
cor(cor_matrix)

vifmodel<-glm(Next.bet.binary~Participant.f
             + sqrtTrial.no 
             + logResult
             + Final.balance
            ,data=modeldata,family=binomial())
vif(vifmodel)
```

## Model

```{r}
model1<-glm(Next.bet.binary~Participant.f
            + sqrtTrial.no
            + logResult
            + logResult:group
            + Final.balance
            -1
            ,data=modeldata,family=binomial())
print.mod.summary(model1,modeldata)
```

## Robust model

```{r}
robmodel1<-glmrob(Next.bet.binary~Participant.f
            + sqrtTrial.no
            + logResult
            + logResult:group
            + Final.balance
            -1
            ,family=binomial, data=modeldata,method="Mqle")
summary(robmodel1)
```

```{r}
robustmodel<-tidy.glmrob(robmodel1,conf.int=TRUE)

robustmodel$OR<-exp(robustmodel$estimate)
robustmodel$OR.low<-exp(robustmodel$conf.low)
robustmodel$OR.high<-exp(robustmodel$conf.high)

write.table(tail(robustmodel,4),"robust_model.csv",sep=",")

data<-(tail(robustmodel,4))
data<-data[,c(1,8,9,10,5)]

data<-rename_cols_for_tables(data)  
data<-rename_rows_for_tables(data)  

filename = "POP1_robmodel_win_BET"
title = "Experiment 1a: Predicting bet size after a win"
pcol="p value"

apa_table(data,filename=filename,pcol=pcol,title=title,column_header=names(data))
```

## Check rob model weights

```{r}
modeldata_withweights<-robmodel_weights(modeldata,robmodel1,'BET')
modeldata$rweights<-modeldata_withweights$rweights

robust_diagnostics(model1,robmodel1)
```

## Diagnostics (log model)

```{r}
nullmodel<-glm(Next.bet.binary~Participant.f -1,data=modeldata,family=binomial())
data4diagnostics<-glmPost(model1,modeldata,nullmodel)
write.table(data4diagnostics,"data_with_diagnostics.csv",sep=",")
```

```{r}
glmPostfigs(model1,data4diagnostics,0)
```
## Predicted probs for plot

```{r}
predicted<-expand.grid(Participant.f=unique(modeldata$Participant.f),
                       group=unique(modeldata$group),
                       logResult=c(1,2,3,4,5,6),
                       Final.balance=c(0,10,20,30,40,50,60),
                       sqrtTrial.no=median(modeldata$sqrtTrial.no))
predicted$predicted<-predict(model1,predicted ,type="response")
write.table(predicted,"matrix_predicted.csv",sep=",")
```

```{r}
predicted<-expand.grid(Participant.f=unique(modeldata$Participant.f),
                       group=unique(modeldata$group),
                       logResult=c(1,2,3,4,5,6),
                       Final.balance=c(0,10,20,30,40,50,60),
                       sqrtTrial.no=median(modeldata$sqrtTrial.no))
predicted$predicted<-predict(robmodel1,predicted ,type="response")
write.table(predicted,"robust_matrix_predicted.csv",sep=",")
```
