---
jupyter:
  jupytext:
    text_representation:
      extension: .Rmd
      format_name: rmarkdown
      format_version: '1.1'
      jupytext_version: 1.2.4
  kernelspec:
    display_name: R
    language: R
    name: ir
---

# POP1 loss model BET
Organised version of New Horizons analysis. DID NOT EXCLUDE p24 now - decided it was wrong to exclude as although finished early, behav before interesting. Has changed loss streak result.

Don't include reference as had previously decided to remove it as became too complicated - reference binary is correlated with balance - another way of describing balance.

This is analysis of bet behaviour (higher or lower than participant median) after a loss outcome. 

Have excluded participants who don't change their bet. 

```{r}
import_library = function(lib_name){
    suppressWarnings(suppressMessages(require(lib_name, character.only = TRUE)))
}

import_library('Hmisc') # for rcorr
import_library('car') # regression diagnostics
import_library('MASS') # residuals?
import_library('boot')
import_library('ggplot2')
import_library('pastecs')
import_library('caTools')
import_library('RColorBrewer')
import_library('corrplot')
import_library('tidyverse')
import_library('IRdisplay')
library(robustbase)
library('extofficer') 

source(file="../../../../../POP_functions.R")
source(file="../../../../../glmPost.R")
```

```{r}
modeldata=load_data('BET', 'loss','POP1')
modeldata<-subset(modeldata,Participant!=40)#After two bets, bet stayed same. Not auto excluded.
```

## Variable correlations

```{r}
cor_matrix<-modeldata[,c("sqrtTrial.no","Final.balance","logLoss.streak")]

cor(cor_matrix)

vifmodel<-glm(Next.bet.binary~Participant.f
             + sqrtTrial.no 
             + Final.balance
             + logLoss.streak
            ,data=modeldata,family=binomial())
vif(vifmodel)
```

## Model

```{r}
model1<-glm(Next.bet.binary~Participant.f
             + sqrtTrial.no
             + Final.balance
             + Final.balance:group
             + logLoss.streak
             + logLoss.streak:group
             -1
            ,data=modeldata,family=binomial())
print.mod.summary(model1,modeldata)
```

## Robust model

```{r}
robmodel1<-glmrob(Next.bet.binary~Participant.f
             + sqrtTrial.no
             + Final.balance
             + Final.balance:group
             + logLoss.streak
             + logLoss.streak:group
             -1,family=binomial, data=modeldata,method="Mqle")
summary(robmodel1)
```

```{r}
robustmodel<-tidy.glmrob(robmodel1,conf.int=TRUE)

robustmodel$OR<-exp(robustmodel$estimate)
robustmodel$OR.low<-exp(robustmodel$conf.low)
robustmodel$OR.high<-exp(robustmodel$conf.high)

write.table(tail(robustmodel,5),"robust_model.csv",sep=",")

data<-(tail(robustmodel,5))
data<-data[,c(1,8,9,10,5)]

data<-rename_cols_for_tables(data)  
data<-rename_rows_for_tables(data)  

filename = "POP1_robmodel_loss_BET"
title = "Experiment 1a: Predicting bet size after a loss"
pcol="p value"

apa_table(data,filename=filename,pcol=pcol,title=title,column_header=names(data))
```

## Robmodel weights

```{r}
modeldata_withweights<-robmodel_weights(modeldata,robmodel1,'BET')
modeldata$rweights<-modeldata_withweights$rweights

robust_diagnostics(model1,robmodel1)
```

## Diagnostics

```{r}
nullmodel<-glm(Next.bet.binary~Participant.f-1,data=modeldata,family=binomial())
data4diagnostics<-glmPost(model1,modeldata,nullmodel)
write.table(data4diagnostics,"data_with_diagnostics.csv",sep=",")
```

```{r}
glmPostfigs(model1,data4diagnostics,0)
```
## Subset model
Participants 15, 24, 72 - most of their trials have high leverage. difficult to know if participants are bad- as leave one out stats only do ind data points

```{r}
subset_modeldata<-subset(modeldata, Participant.f!= 15 | Participant.f!= 24 | Participant.f!= 72)

robmodel1b<-glmrob(Next.bet.binary~Participant.f
             + sqrtTrial.no
             + Final.balance
             + Final.balance:group
             + logLoss.streak
             + logLoss.streak:group
             -1,family=binomial, data=subset_modeldata,method="Mqle")
summary(robmodel1b)
```

## Predicted probs for plotting

```{r}
predicted<-expand.grid(Participant.f=unique(modeldata$Participant.f),
                       group=unique(modeldata$group),
                       Final.balance=c(0,10,20,30,40,50,60),
                       logLoss.streak=c(0,1,2,3,4),
                       sqrtTrial.no=median(modeldata$sqrtTrial.no))
predicted$predicted<-predict(robmodel1,predicted ,type="response")
write.table(predicted,"robust_matrix_predicted.csv",sep=",")
```

```{r}
predicted<-expand.grid(Participant.f=unique(modeldata$Participant.f),
                       group=unique(modeldata$group),
                       Final.balance=c(0,10,20,30,40,50,60),
                       logLoss.streak=c(0,1,2,3,4),
                       sqrtTrial.no=median(modeldata$sqrtTrial.no))
predicted$predicted<-predict(model1,predicted ,type="response")
write.table(predicted,"matrix_predicted.csv",sep=",")
```
