Tst for sig diffs between summary variables - 5 min spend, total spend, final  balance, average bet size.

```{r setup, include=FALSE}

library(Hmisc)
library(pastecs)
library(dplyr)

rfromwilcox<-function(wilcoxModel,N){
  z<-qnorm(wilcoxModel$p.value/2)
  r<-z/sqrt(N)
  cat(wilcoxModel$data.name,"Effect size, r = " , r)
  
}

```

## Data prep
Load data, create binary group variable, exlude participants who didn't follow instructions,

```{r data prep}

data=read.csv("../../data_for_analysis/POP2_participant_summary_variables.csv")

#data<-subset(data, Participant.ID!=)# faulty recording
data$group<-data$Earned

data$mode<-ifelse((data$Game_mode)=="CASH",0,1)

sum(data$group) # out of 50
by(data$mode,data$group,sum)

```

```{r}
trial_data=read.csv("../../data_for_analysis/all_participants_trial_data.csv")
#trial_data<-subset(trial_data,Participant != )

mean.bet<-as.data.frame(do.call("rbind",by(trial_data$Bet.amount,trial_data$Participant,stat.desc,basic=TRUE)))
data$mean.bet<-mean.bet$mean

total.won<-as.data.frame(do.call("rbind",by(trial_data$Result,trial_data$Participant,stat.desc,basic=TRUE)))
data$total.won<-total.won$sum

five_min_trial_data<-subset(trial_data,Time.of.bet.relative.to.first.bet<300)
total.won.by.5.min<-as.data.frame(do.call("rbind",by(five_min_trial_data$Result,five_min_trial_data$Participant,stat.desc,basic=TRUE)))
data$total.won.by.5.min<-total.won.by.5.min$sum

data$Total.wager<-data$Total.wager.by.5.minutes+data$Total.wager.after.5.minutes
```


## PGSI

```{r check characteristics matched}

by(data$PGSI,data$group,stat.desc,basic=TRUE,norm=TRUE)
PGSI_model<-wilcox.test(data$PGSI~data$group,paired=FALSE,exact=FALSE,na.action = na.exclude)# turn off exact as get error that cant do it
PGSI_model
rfromwilcox(PGSI_model,50) #df = n in group1 -1 + n in group 2 -1



```
## Age

```{r}
by(data$Age,data$group,stat.desc,basic=TRUE,norm=TRUE)
Age_model<-wilcox.test(data$Age~data$group,paired=FALSE,exact=FALSE,na.action = na.exclude)# turn off exact as get error that cant do it
Age_model
rfromwilcox(Age_model,49) #df = n in group1 -1 + n in group 2 -1


```

## Gender

```{r}
temp<-subset(data,Gender!=3)
summarise(group_by(temp,group,Gender),count =n())

# warning due to small N
chisq.test(table(temp$group, temp$Gender))
```

```{r mean bet}
by(data$mean.bet,data$group,stat.desc,basic=TRUE,norm=TRUE)
mean.bet_model<-wilcox.test(data$mean.bet~data$group,paired=FALSE,exact=FALSE,na.action = na.exclude)# turn off exact as get error that cant do it
mean.bet_model
rfromwilcox(mean.bet_model,50) #df = n in group1 -1 + n in group 2 -1
```

#Pre-reg models
Are 5 min and total spend correlated? 
Total spend includes some measure of persistance - as includes periods when choose whether or not to play. 5 min includes the earlier period of play when people are 'forced' to play and have least variance in current balance. Originally used 10 mins but decided to go back to Candy's anlaysis of 5 mins. No sig diff either way but brings in line with POP2 plan.
```{r}
corr_matrix<-data.frame(data$Total.wager.by.5.minutes,data$Total.wager)
rcorr(as.matrix(corr_matrix))   

corr_matrix<-data.frame(data$total.won.by.5.min,data$Balance.at.5.minutes)
rcorr(as.matrix(corr_matrix))   
```

## Five min spend. 
```{r 5 min spend}
by(data$Total.wager.by.5.minutes,data$group,stat.desc,basic=TRUE,norm=TRUE)
Total.wager.by.5.minutes_model<-wilcox.test(data$Total.wager.by.5.minutes~data$group,paired=FALSE,exact=FALSE,na.action = na.exclude)# turn off exact as get error that cant do it
Total.wager.by.5.minutes_model
rfromwilcox(Total.wager.by.5.minutes_model,50) #df = n in group1 -1 + n in group 2 -1
 
```
## Total spend
```{r total spend}
by(data$Total.wager,data$group,stat.desc,basic=TRUE,norm=TRUE)
Total.wager_model<-wilcox.test(data$Total.wager~data$group,paired=FALSE,exact=FALSE,na.action = na.exclude)# turn off exact as get error that cant do it
Total.wager_model
rfromwilcox(Total.wager_model,50) #df = n in group1 -1 + n in group 2 -1
```

```{r}
by(data$Final.balance,data$group,stat.desc,basic=TRUE,norm=TRUE)
Final.balance_model<-wilcox.test(data$Final.balance~data$group,paired=FALSE,exact=FALSE,na.action = na.exclude)# turn off exact as get error that cant do it
Final.balance_model
rfromwilcox(Final.balance_model,50) #df = n in group1 -1 + n in group 2 -1
```

```{r}
by(data$slot_spend_month,data$group,stat.desc,basic=TRUE,norm=TRUE)
slot_spend_month_model<-wilcox.test(data$slot_spend_month~data$group,paired=FALSE,exact=FALSE,na.action = na.exclude)# turn off exact as get error that cant do it
slot_spend_month_model
rfromwilcox(slot_spend_month_model,49) #df = n in group1 -1 + n in group 2 -1

```

```{r}

```
