---
jupyter:
  jupytext:
    text_representation:
      extension: .Rmd
      format_name: rmarkdown
      format_version: '1.1'
      jupytext_version: 1.2.4
  kernelspec:
    display_name: R
    language: R
    name: ir
---

# POP1 win model ISI
Fixed effects regression of ITI from slots tracker.

```{r}
import_library = function(lib_name){
    suppressWarnings(suppressMessages(require(lib_name, character.only = TRUE)))
}
import_library('Hmisc') # for rcorr
import_library('car') # regression diagnostics
import_library('MASS') # residuals?
import_library('boot')
import_library('ggplot2')
import_library('pastecs')
import_library('caTools')
import_library('RColorBrewer')
import_library('corrplot')
import_library('tidyverse')
import_library('robustbase')
library('extofficer') 


source(file="../../../../../POP_functions.R")
source(file="../../../../../glmPost.R")
```

```{r}
modeldata=load_data('ISI', 'win','POP1')
```

## Predictor Correlations and VIF
VIF not a problem for factors with more than three levels or interactions (https://www.statisticshowto.com/variance-inflation-factor/).
Multicollinearity increases variance of stat - VIF = by how much is it inflated compared to if no multiC. Means that we may miss sig effects. But this OK as we want to err on side of caution anyway.

```{r}
cor_matrix<-modeldata[,c("sqrtTrial.no","logResult","Final.balance")]
cor(cor_matrix)

vifmodel<-lm(logISI~Participant.f
            + sqrtTrial.no
            + Final.balance
            + logResult 
            ,data=modeldata)
vif(vifmodel)
```

##  Log Model

```{r}
logmodel1<-glm(logISI~Participant.f
             + sqrtTrial.no 
             + Binary.bet.change
             + logResult
             + logResult:group
             + Final.balance
             -1
            ,data=modeldata,family=gaussian)
print.mod.summary(logmodel1,modeldata)
```

## Robust log model
Using robustbase.
KS2014 recomended setting in robustbase.pdf - good for models with factors, particialry when some levels have small sample (previously I think these would have been deweighted too much)
fast.s.large.n = Inf stops the large n straegy - which fails (I think something to do with splitting data). We don;t want to split data, and it errors when try. Only happen with loss ata - when eeoigh rows to try split

```{r}
robmodel1<-lmrob(logISI~Participant.f
             + sqrtTrial.no 
             + Binary.bet.change
             + logResult
             + logResult:group
             + Final.balance
             -1
            ,data=modeldata,control=lmrob.control(fast.s.large.n = Inf,setting="KS2014"))
summary(robmodel1)
```
```{r}
robustmodel<-tidy.glmrob(robmodel1,conf.int=TRUE)
write.table(tail(robustmodel,5),"POP1_robust_model.csv",sep=",")

data<-(tail(robustmodel,5))
data<-data[,c(1,2,6,7,5)]

data<-rename_cols_for_tables(data)  
data<-rename_rows_for_tables(data)  

filename = "POP1_robmodel_win_ISI"
title = "Experiment 1a: Predicting spin iniitation latency after a win"
pcol="p value"

apa_table(data,filename=filename,pcol=pcol,title=title,column_header=names(data))

```

## Check weight properties

```{r}
modeldata_withweights<-robmodel_weights(modeldata,robmodel1,'ISI')
modeldata$rweights<-modeldata_withweights$rweights

robust_diagnostics(logmodel1,robmodel1) #prints image files to folder
```

## Diagnostics (log model)

```{r}
nullmodel<-glm(logISI~Participant.f-1,data=modeldata,family=gaussian)
data4diagnostics<-glmPost(logmodel1,modeldata,nullmodel)
write.table(data4diagnostics,"data_with_diagnostics.csv",sep=",")
```

```{r}
glmPostfigs(logmodel1,data4diagnostics,0)
```

## Predicted for plotting

```{r}
predicted<-expand.grid(Participant.f=unique(modeldata$Participant.f),
                       group=unique(modeldata$group),
                       logResult=c(1,2,3,4,5,6),
                       Final.balance=c(0,10,20,30,40,50,60),
                       sqrtTrial.no=median(modeldata$sqrtTrial.no),
                       Binary.bet.change=0)
predicted$predicted<-predict(logmodel1,predicted ,type="response")
write.table(predicted,"matrix_predicted.csv",sep=",")

predicted<-expand.grid(Participant.f=unique(modeldata$Participant.f),
                       group=unique(modeldata$group),
                       logResult=c(1,2,3,4,5,6),
                       Final.balance=c(0,10,20,30,40,50,60),
                       sqrtTrial.no=median(modeldata$sqrtTrial.no),
                       Binary.bet.change=0)
predicted$predicted<-predict(robmodel1,predicted ,type="response")
write.table(predicted,"robust_matrix_predicted.csv",sep=",")

```

## Reverse model
Not neede  no group effects


## Outlier removal as pre-reg

```{r}
source(file="../../../../../MRtrim.R")
RT_data<-data.frame(modeldata$X,modeldata$Participant,modeldata$Binary.bet.change,modeldata$logISI)
names(RT_data) <- c("Trial","Participant","condition","RT")
MRtrimoutput<-MRtrim(RT_data,0,5)#call RT trimming function - 
                                    #don't removed min, or if sample size < 5

data_with_modRT<-cbind(modeldata,MRtrimoutput$trimmed_data_withNAs)
data_with_modRT$removed<-(is.na(data_with_modRT$mod_RT)==TRUE)
data_trimmed<-data_with_modRT[complete.cases(data_with_modRT[ , "mod_RT"]),]

removedTrials<-data_with_modRT[is.na(data_with_modRT$mod_RT),]

write.table(MRtrimoutput$removedCount,"removed_trials_count.csv",sep=",")
write.table(MRtrimoutput$removedTrials,"removed_trials.csv",sep=",")

#print which participants were skipped by MRtrim (count=NA)
smallNconditions<-MRtrimoutput$removedCount[is.na(MRtrimoutput$removedCount$count),]
write.table(smallNconditions,"smallNparticipants.csv",sep=",")

cat("Percent trials removed:              ",(nrow(removedTrials)/nrow(data))*100,"\n")
cat("N trials in trimmed data:            ",nrow(data_trimmed),"\n")
cat("N trials in original data:           ",nrow(modeldata),"\n")
cat("N trials removed:                    ",nrow(removedTrials),"\n\n")

cat("Bet change trials in original data:  ",nrow(subset(modeldata,Binary.bet.change==1)),"\n")
cat("Removed bet change trials:           ",nrow(subset(removedTrials,Binary.bet.change==1)),"\n")
```

```{r}

robmodel2<-lmrob(logISI~Participant.f
             + sqrtTrial.no 
             + Binary.bet.change
             + logResult
             + logResult:group
             + Final.balance
             #+ Final.balance:group
             -1
            ,data=data_trimmed,control=lmrob.control(fast.s.large.n = Inf,setting="KS2014"))
summary(robmodel2)
```

## Game mode
Not needed no group effects

```{r}

```
