---

---

# Summary stats for POP 1
### Eve Limbrick-Oldfield
#### 20/06/2018

Test for sig diffs between summary variables - 5 min spend, total spend, final  balance, average bet size.


```{r}
library(Hmisc)
library(pastecs)
library(dplyr)
rfromwilcox<-function(wilcoxModel,N){
  z<-qnorm(wilcoxModel$p.value/2)
  r<-z/sqrt(N)
  cat(wilcoxModel$data.name,"Effect size, r = " , r)
  }
#install.packages("remotes")
#remotes::install_github("rettopnivek/extofficer")
```

### Data prep

```{r}
#Load data, create binary group variable, exlude participants who didn't follow instructions,

data=read.csv("../../data_for_analysis/POP1_participant_summary_variables.csv")

data$group<-data$Cash
data$group<-ifelse(is.na(data$group)==TRUE,0,1)
trial_data=read.csv("../../data_for_analysis/all_participants_trial_data.csv")
mean.bet<-as.data.frame(do.call("rbind",by(trial_data$Bet.amount,trial_data$Participant,stat.desc,basic=TRUE)))
data$mean.bet<-mean.bet$mean

data$Total.won<-data$Total.wager.by.10.minutes+data$Total.wager.after.10.minutes
data$Total.wager<-data$Total.wager.by.10.minutes+data$Total.wager.after.10.minutes

unique_table<-data %>% distinct(Participant.ID, .keep_all = TRUE)
cat('\n\nIncluded participants:\n',unique_table$Participant.ID)
n_per_gp<-unique_table %>% group_by(group) %>% tally()
cat('\n\n')
print(n_per_gp)  

```

## Number of bets AND LAST BET TIME per participant for QC and exclusions

```{r}
new_aggregates<-setNames(aggregate(Time.of.bet.relative.to.first.bet ~ Participant, data = trial_data, max),c("Participant","Time"))
Nbets_per_participant<-setNames(aggregate(Trial.no ~ Participant, data = trial_data, max),c("Participant","Nbets"))
new_aggregates$Nbets<-Nbets_per_participant$Nbets
new_aggregates$Final_balance<-data$Final.balance

print("Participants who finished before 10 mins")
subset(new_aggregates,Time<600)

write.csv(new_aggregates,"POP1_Nbets_and_last_bet_time.csv", row.names = FALSE)

```

### Are any variables correlated?

## Pairwise group comparisons - traits

Group 0 = Cash

### Age
3 missing


```{r}
#DV (age) IV (group)
by(data$Age,data$group,stat.desc,basic=TRUE,norm=TRUE)
Age_model<-wilcox.test(data$Age~data$group,paired=FALSE,exact=FALSE,na.action = na.exclude)# turn off exact as get error that cant do it
Age_model
rfromwilcox(Age_model,56) #df = n in group1 -1 + n in group 2 -1

```

### Sex
Male = 1, female = 2

```{r}
summarise(group_by(data,group,Gender),count =n())
chisq.test(table(data$group, data$Gender))
```

### PGSI

```{r}
by(data$PGSI,data$group,stat.desc,basic=TRUE,norm=TRUE)
PGSI_model<-wilcox.test(data$PGSI~data$group,paired=FALSE,exact=FALSE,na.action = na.exclude)# turn off exact as get error that cant do it
PGSI_model
rfromwilcox(PGSI_model,59) #df = n in group1 -1 + n in group 2 -1

```

### Slot spend month

```{r}
by(data$slot_spend_month,data$group,stat.desc,basic=TRUE,norm=TRUE)
slot_spend_month_model<-wilcox.test(data$slot_spend_month~data$group,paired=FALSE,exact=FALSE,na.action = na.exclude)# turn off exact as get error that cant do it
slot_spend_month_model
rfromwilcox(slot_spend_month_model,59) #df = n in group1 -1 + n in group 2 -1

```

## Pairwise comparisons: slot behaviour


### Mean bet amount 

```{r}
# Exclude early cash out 
data<-subset(data,Participant.ID != 24) # didn't gamable for required time
```

```{r}
by(data$mean.bet,data$group,stat.desc,basic=TRUE,norm=TRUE)
mean.bet_model<-wilcox.test(data$mean.bet~data$group,paired=FALSE,exact=FALSE,na.action = na.exclude)# turn off exact as get error that cant do it
mean.bet_model
rfromwilcox(mean.bet_model,58) #df = n in group1 -1 + n in group 2 -1
```

### Final balance

```{r}
#compare final balance between groups: not normal. Not sig. But trend for cash>credit.
by(data$Final.balance,data$group,stat.desc,basic=TRUE,norm=TRUE)
Final.balance_model<-wilcox.test(data$Final.balance~data$group,paired=FALSE,exact=FALSE,na.action = na.exclude)# turn off exact as get error that cant do it
Final.balance_model
rfromwilcox(Final.balance_model,58) #df = n in group1 -1 + n in group 2 -1
```

### Five min spend. 

```{r}
by(data$Total.wager.by.5.minutes,data$group,stat.desc,basic=TRUE,norm=TRUE)
Total.wager.by.5.minutes_model<-wilcox.test(data$Total.wager.by.5.minutes~data$group,paired=FALSE,exact=FALSE,na.action = na.exclude)# turn off exact as get error that cant do it
Total.wager.by.5.minutes_model
rfromwilcox(Total.wager.by.5.minutes_model,58) #df = n in group1 -1 + n in group 2 -1
```

### Total spend

```{r}
by(data$Total.wager,data$group,stat.desc,basic=TRUE,norm=TRUE)
Total.wager_model<-wilcox.test(data$Total.wager~data$group,paired=FALSE,exact=FALSE,na.action = na.exclude)# turn off exact as get error that cant do it
Total.wager_model
rfromwilcox(Total.wager_model,58) #df = n in group1 -1 + n in group 2 -1
```
